cardinalR: Generating interesting high-dimensional data structures

### 2025-08-23 paper-cardinalR.Rmd
Added langevitour views of the data in HTML view

```{r, eval=FALSE}
langevitour::langevitour(gridcube)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(unifcube)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(cubehole)
```

@@

```{r, label = "fig-cube-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.", fig.width=15, fig.height=15}

@@

```{r, eval=FALSE}
langevitour::langevitour(quadratic)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(cubic)
```

@@

```{r, label = "fig-cubic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.", fig.width=15, fig.height=10}

@@

```{r, eval=FALSE}
langevitour::langevitour(pyrrect)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(pyrtri)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(pyrstar)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(pyrholes)
```

@@

```{r, label = "fig-pyr-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.", fig.width=15, fig.height=20}

@@

```{r, eval=FALSE}
langevitour::langevitour(circle)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(curvycycle)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(unifsphere)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(gridedsphere)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(clusteredspheres)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(hemisphere)
```

@@

```{r, label = "fig-sphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

@@

```{r, eval=FALSE}
langevitour::langevitour(crescent)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(curvycylinder)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(sphericalspiral)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(helicalspiral)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(conicspiral)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(nonlinear)
```

@@

```{r, label = "fig-triginometric-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

>>>>

```{r}
gridcube_lang <- langevitour::langevitour(gridcube, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
unifcube_lang <- langevitour::langevitour(unifcube, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
cubehole_lang <- langevitour::langevitour(cubehole, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r cube, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `gridcube`, `unifcube`, and `cubehole` data in $4\\text{-}D$."}

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    gridcube_lang, unifcube_lang, cubehole_lang
  ),
  device = "xs"
)

```{r cube-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.", fig.width=15, fig.height=15}

@@

```{r}
quadratic_lang <- langevitour::langevitour(quadratic, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
cubic_lang <- langevitour::langevitour(cubic, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r poly, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `quadratic` and `cubic` data in $4\\text{-}D$."}

polyfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    quadratic_lang, cubic_lang
  ),
  device = "xs"
)

class(polyfig) <- c(class(polyfig), "htmlwidget")

polyfig
```

```{r poly-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.", fig.width=15, fig.height=10}

@@

```{r}
pyrrect_lang <- langevitour::langevitour(pyrrect, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
pyrtri_lang <- langevitour::langevitour(pyrtri, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
pyrstar_lang <- langevitour::langevitour(pyrstar, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
pyrholes_lang <- langevitour::langevitour(pyrholes, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r pyr, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data in $4\\text{-}D$."}

pyrfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    pyrrect_lang, pyrtri_lang, pyrstar_lang, pyrholes_lang
  ),
  device = "xs"
)

class(pyrfig) <- c(class(pyrfig), "htmlwidget")

pyrfig
```

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.", fig.width=15, fig.height=20}

@@

```{r}
circle_lang <- langevitour::langevitour(circle, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
curvycycle_lang <- langevitour::langevitour(curvycycle, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
unifsphere_lang <- langevitour::langevitour(unifsphere, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
gridedsphere_lang <- langevitour::langevitour(gridedsphere, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
clusteredspheres_lang <- langevitour::langevitour(clusteredspheres, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
hemisphere_lang <- langevitour::langevitour(hemisphere, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r sphere, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `circle`, `curvycycle`, `unifsphere`, `gridedsphere`, `clusteredspheres`, and `hemisphere` data in $4\\text{-}D$."}

spherefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    circle_lang, curvycycle_lang, unifsphere_lang, gridedsphere_lang, clusteredspheres_lang, hemisphere_lang
  ),
  device = "xs"
)

class(spherefig) <- c(class(spherefig), "htmlwidget")

spherefig
```

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

@@

```{r}
crescent_lang <- langevitour::langevitour(crescent, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
curvycylinder_lang <- langevitour::langevitour(curvycylinder, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
sphericalspiral_lang <- langevitour::langevitour(sphericalspiral, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
helicalspiral_lang <- langevitour::langevitour(helicalspiral, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
conicspiral_lang <- langevitour::langevitour(conicspiral, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
nonlinear_lang <- langevitour::langevitour(nonlinear, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r triginometric, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of tthe `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data in $4\\text{-}D$."}

triginometricfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    crescent_lang, curvycylinder_lang, sphericalspiral_lang, helicalspiral_lang, conicspiral_lang, nonlinear_lang
  ),
  device = "xs"
)

class(triginometricfig) <- c(class(triginometricfig), "htmlwidget")

triginometricfig
```

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

### 2025-08-23 paper-cardinalR.tex
Added langevitour views of the data in HTML view

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.}\label{fig:fig-cube-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.}\label{fig:fig-cubic-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyr-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.}\label{fig:fig-pyr-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-sphere-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.}\label{fig:fig-sphere-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-triginometric-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.}\label{fig:fig-triginometric-proj}
\end{figure}

>>>>

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/cube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.}\label{fig:cube-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/poly-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.}\label{fig:poly-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/pyr-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.}\label{fig:pyr-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/sphere-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.}\label{fig:sphere-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/triginometric-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.}\label{fig:triginometric-proj}
\end{figure}
